Discrete Ordinates

### 2016-12-01 docprep/draft1.tex
Added the external source to the sweep code

  # Knowns
  (*$V(r)$*)  # [cm^3] volume of cell ijk
  (*$A_{xy}(\Omega,i,j), A_{yz}(\Omega,j,k), A_{xz}(\Omega,i,k)$*)  # [cm^2] Area of each face of cell ijk
  # Unknowns
  (*$\phi(r, E) = \vec{0}$*)    # Scalar flux
  (*$\Psi(r, \Omega, E) = \vec{0}$*)  # Angular flux

>>>>

  # Knowns
  (*$V(r)$*)  # [cm^3] Volume of cell ijk
  (*$A_{xy}(\Omega,i,j), A_{yz}(\Omega,j,k), A_{xz}(\Omega,i,k)$*)  # [cm^2] Area of each face of cell ijk
  (*$S_x(E, r)$*)  # [#] External source
  # Unknowns
  (*$\phi(r, E) = \vec{0}$*)    # Scalar flux
  (*$\Psi(r, \Omega, E) = \vec{0}$*)  # Angular flux
